Verification of the CVM algorithm with a Functional Probabilistic Invariant

### 2025-07-04 paper/main.tex
Paper: Fixes suggested by Yong Kiam.

@@

We call inequalities like Inequality~\ref{i:func_invariant} and \ref{i:func_invariant_capped}: \emph{functional probabilistic invariants}.
The inequalities can be established using induction over the steps of the randomized algorithm.
Even, though, the actual distribution of the states themselves are not known, nor do we think it is possible to find useful closed form descriptions for them, the invariant establishes valuable information about the distribution of the state. In this case, enough information, to establish exponential tail bounds for the algorithm.

>>>>

\nolinenumbers

@@

We call inequalities like Inequality~\ref{i:func_invariant} and \ref{i:func_invariant_capped}: \emph{functional probabilistic invariants}.
The inequalities can be established using induction over the steps of the randomized algorithm.
Even though the actual distribution of the states themselves are not known, nor do we think it is possible to find useful closed form descriptions for them, the invariant establishes valuable information about the distribution of the state. In this case, enough information, to establish exponential tail bounds for the algorithm.
